Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
evd results process is getting there.

@@

fevd(b, threshold = 170, type = "GP")

>>>>

1. Make threshold plot to figure out threshold
2. Make associated mean excess plot
3. Calculate the 95% quantile for mean excess to use as threshold
4. Make threshplot and show the threshold based on the mean excess
5. fit a gpd distribution using that threshold and report parameter values
6. Calculate conditional probabilities over certain distances

@@

fit <- fevd(b, threshold = 170, type = "GP")
plot(fit)
fit$results

1-pevd(1000,threshold = 170, scale= fit$results$par[1], shape = fit$results$par[2], type = "GP")

# OR

dist_range <- c(1000, 5000, 10000)
pextRemes(fit, dist_range, lower.tail = FALSE)
